---
title       : Predicting MPG
subtitle    : Based on mtcars
author      : Pep Carrera
job         : Student in Coursera
framework   : io2012
highlighter : highlight.js
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

1. Our Application attemptes to predict MPG
2. The Prediction is based on a model that uses the mtcars data set
3. Over the next few slides you will see the model, and understand how we use it and the user inputs to easily predict your car's miles per gallon!

--- .class #id 

## The data

1. We use the mtcars data set
2. Below you'll see a snapshot of the mtcars data
3. As you can see there are many variables, however our best model that predicts mpg uses cyl (cylinders), hp (horse power), wt (weight, lbs divided by 1000), and am (is it automatic or manual)

```{r}
data(mtcars)
head(mtcars)
```
---

## The model

1. As previously explained, we use the 4 key data elements, but we need to do some lite data processing
2. We'll make am and cyl factors
3. Next you'll see us fit the model on the data set

```{r}
mtcars$am <- factor(mtcars$am)
mtcars$cyl <- factor(mtcars$cyl)

# Create model predicting mpg based on cylinder, horse power, weight, and transmission type (am)
modelFit <- lm(mpg ~ cyl + hp + wt + am, data = mtcars)
```

---

## Predicting Miles Per Gallon

1. Here we show you the prediction function that the application takes advatnage of
2. First we create a dataframe with data from a 2010 Ford Mustang (V6 Automatic)

```{r}
newdata <- data.frame(cyl=6, hp=210, wt=3401/1000, am=1)
newdata$am <- factor(newdata$am)
newdata$cyl <- factor(newdata$cyl)
```

---

## The Results

1. We run the predict function on the data
2. Our function predicts 17.25 MPG (The actual is 19)
3. As you can see this is a great application to predict MPG simply based on targets for a car
4. Check out or app here: https://pepcarrera.shinyapps.io/Developing-Data-Products

5. Here is the Ford Mustang MPG official page: 

http://www.fueleconomy.gov/feg/noframes/26348.shtml

```{r}
predict(modelFit,newdata=newdata)
```

